\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-24 tex/overview.tex
add section demonstrating that the most dynamically robust network architectures have a single type of SCC

>>>>

\subsection{The most dynamically robust network architectures have a single type of SCC}
The previously considered optimization problem maximized dynamical robustness subject to the constraint that the network have a particular set of SCCs.  We will now generalize this to situations in which we fix the types of SCCs which may appear in our network, but allow arbitrary numbers of each type.  We will study the constrained optimization problem where we fix the total number of nodes to constant $N$. This analysis will show that the most dynamically robust networks will be homogeneous in the types of their SCCs thereby having only a single type. This result drastically limits the number of different networks on $N$ nodes that are candidates for being the most dynamically robust.

Suppose that ${\hat C}_1, \ldots, {\hat C}_n$ is a collection of non-isomorphic strongly connected directed graphs and that $G$ is a directed graph such that every SCC of $G$ is isomorphic to some ${\hat C}_i$ for some $i$.  For all $i \in \{1, \ldots, n\}$, let $k_i$ be the number of SCCs of $G$ which are isomorphic to ${\hat C}_i$.  Then, following algebraic manipulation, \ref{eq:robschematic} can be rewritten as follows:
\begin{equation}\label{eq:robtype}
1-R(G) = \frac{\sum_{i=1}^n k_i d_i (1-R_i)}{l + \sum_{i=1}^n k_i d_i}.
\end{equation}
Maximizing $R$ is equivalent to minimizing $1-R$.  Even though the $k_i$'s are integer variables, we will approximate them as positive real variables.  The accuracy of this approximation increases in the limit of large networks.

When maximizing robustness subject to a fixed number $N$ of nodes, we can make use of our previous result in \ref{eq:sccmaxrobustness} to restrict attention to directed graphs with the maximal number of links between SCCs.  Hence, we can replace $l$ with $l_{\mathrm{max}}$ in \ref{eq:robtype} to obtain
\begin{equation}
1-R(G) = \frac{\sum_{i=1}^n k_i d_i (1-R_i)}
  {\frac{1}{2} N^2 - \frac{1}{2} \sum_{i=1}^n k_i v_i^2 + \sum_{i=1}^n k_i d_i} .
\end{equation}
The condition on the total number of nodes means that the $k_i$'s cannot be varied independently but are subject to the constraint $\sum_{i=1}^n k_i v_i = N$.  Geometrically, this constraint defines a hyperplane and the interesection of this hyperplane with the positive orthant is the simplex whose vertices are the points $(N/v_1, 0, \ldots, 0), (0, N/v_2, \ldots, 0), \ldots, (0, 0, \ldots, N/v_n)$.

Since both numerator and denominator are linear in the variables $k_i$ over which we are optimizing, an elementary argument shows the quantity will assume its minimum value at one of the vertices of the simplex.
The value at the $i$-th vertex equals
\begin{equation}
 q_i =
 \frac{2 d_i (1 - R_i)}
      {(k_i - 1) v_i^2 + 2 d_i},
\end{equation}
hence the network which maximizes robustness will have as many SCCs as possible be of the type which have the smallest value of $q_i$.
